Reviewer Comments (Scientific Reports)

### 2020-03-23 notebook/sci_rep_reviews.Rmd
Adjust the line numbers for the new revision and finish addressing the comments from Reviewer 3

I have explained the result shown by the black line of Figures 3 (now 4), and the former figure 4 (now in the SI), now more clearly in my revision (L417).

@@

Theoretical studies of community stability assign negative diagonal values (typically -1) to make the simplifying assumption that components of the system are self-regulating (e.g., May 1972, 1973; Sinha 2005; Allesina and Tang 2012; Grilli et al. 2017; Song and Saavedra 2018; Stone 2018). If individual components are not self-regulating, then the system will almost never be stable. I tried this very early on in the process of investigating the effects of $\gamma$ by allowing diagonal elements to be sampled in the same way as off-diagonals: from a normal distribution centred at zero (data are here, note that the tables show the information in a bit more of a confusing format that in the SI, which was subsequently improved prior to submission: https://github.com/bradduthie/RandomMatrixStability/blob/dfe6f8e0225733c94348bc9e0dad6218c59cc109/notebook/sim_results_old/oldest/mat_dat.csv). The effect of $\gamma$ on increasing stability is retained, but stability of all systems drops to zero out of one million given size $S > 14$. And in the random systems that are found to be stable, all diagonal elements are nearly always negative (or, rarely, with one or two very low positive values). In other words, if diagonal elements were randomly sampled from a distribution with positive support, then the only systems that would be stable would be those that by chance had all (or nearly all) negative diagonal elements.

@@

I have tried to clarify and more clearly state the assumption of self-regulation in my revision (line XXX).

@@

I have tried to clarify the role of random matrices as a null model of complex system stability (line XXX).

@@

Component response rates can be modelled using a diagonal matrix in which elements correspond to the rate at which individual system components respond to perturbations in the system (Patel et al. 2018). Hence, such a diagonal matrix $\gamma$ can be multiplied by a random matrix representing a complex system $A$ to produce a complex system in which component response rates vary, $M = \gamma A$. By doing an eigenanalysis on $M$ versus $A$, it is possible to understand how response rates affect stability. Hence, I am not comparing apples and oranges; response rates of components have a clear and important role in complex system stability that can be investigated with the mathematical techniques used in this manuscript. I have tried to explain this role more clearly in my revision (line XXX).

@@

I thank Reviewer 3 for pointing out these articles. I have cited them where appropriate (lines XXX).

>>>>

I have explained the result shown by the black line of Figures 3 (now 4), and the former figure 4 (now in the SI), now more clearly in my revision (L420).

@@

Theoretical studies of community stability assign negative diagonal values (typically -1) to make the simplifying assumption that components of the system are self-regulating (e.g., May 1972, 1973; Sinha 2005; Allesina and Tang 2012; Grilli et al. 2017; Song and Saavedra 2018; Stone 2018). If individual components are not self-regulating, then the system will almost never be stable. I tried this very early on in the process of investigating the effects of $\gamma$ by allowing diagonal elements to be sampled in the same way as off-diagonals: from a normal distribution centred at zero (data are here, note that the tables show the information in a bit more of a confusing format that in the SI, which was subsequently improved prior to my original submission: https://github.com/bradduthie/RandomMatrixStability/blob/dfe6f8e0225733c94348bc9e0dad6218c59cc109/notebook/sim_results_old/oldest/mat_dat.csv). The effect of $\gamma$ on increasing stability is retained, but stability of all systems drops to zero out of one million given size $S > 14$. And in the random systems that are found to be stable, all diagonal elements are nearly always negative (or, rarely, with one or two very low positive values). In other words, if diagonal elements were randomly sampled from a distribution with positive support, then the only systems that would be stable would be those that by chance had all (or nearly all) negative diagonal elements.

@@

I have tried to clarify and more clearly state the assumption of self-regulation in my revision (paragraphs starting on L28 and L65).

@@

I have tried to clarify the role of random matrices as a null model of complex system stability (L53-L64).

@@

Component response rates can be modelled using a diagonal matrix in which elements correspond to the rate at which individual system components respond to perturbations in the system (Patel et al. 2018). Hence, such a diagonal matrix $\gamma$ can be multiplied by a random matrix representing a complex system $A$ to produce a complex system in which component response rates vary, $M = \gamma A$. By doing an eigenanalysis on $M$ versus $A$, it is possible to understand how response rates affect stability. Hence, I am not comparing apples and oranges; response rates of components have a clear and important role in complex system stability that can be investigated with the mathematical techniques used in this manuscript. I have tried to explain this role more clearly in my revision by more clearly presenting results in terms of differences between the matrices $A$ and $M$ (this affected many areas throughout the text and SI, with clarification of the comparison presented in L82-L89).

@@

I thank Reviewer 3 for pointing out these articles. I have cited them where appropriate (L25, L69, L323, L325, and L367).
